Hochschild cohomology of torus equivariant D-modules

### 2017-10-10 paper.tex
Put all macros into the file.
Acknowledgements

\title{Hochschild cohomology of torus-equivariant D-modules}
\author{Clemens Koppensteiner}

\usepackage{math-gl}

@@

\let\stack\mathbf
\let\shortbar\bar
\let\bar\overline

%\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
\newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathup{mon}}}
\newcommand\catDModHolMon[2]{\catDModHol{#1}^{#2-\mathup{mon}}}

\newcommand\dR{\mathrm{dR}}
\newcommand{\renstar}{\blacktriangle}

\newcommand{\HCoh}{\operatorname{HH}^\cx}
\newcommand\GammadR{Γ_{\mkern-4mu\dR}}

\newcommand\opalg[1]{#1^{\mathrm{op}}}

\renewcommand\B{\stack{B}}
\newcommand\mappingstack{\mathbfup{Maps}}
\newcommand\X{\mathbb{X}}

\newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
\newcommand\barGammasub[1]{\bar{\Gamma}_{\mkern-3mu#1}}

\newcommand\XXtimes{%
    \mathchoice%
        {\mathop{×}\limits_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
    }
\renewcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}

@@

\newcommand\stabls[2]{L^{#1}#2}
\newcommand\stabcls[2]{\overline{L}^{#1}#2}
\newcommand\stablsc[2]{L^{#1,c}#2}
\newcommand\stablsY[3][\stack Y]{L_{#1}^{#2}#3}
\newcommand\stabclsY[3][\stack Y]{\overline{L}_{#1}^{#2}#3}
\newcommand\stablscY[3][\stack Y]{L_{#1}^{#2,c}#3}

\newcommand\Stab{\operatorname{Stab}}

\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}
\newcommand\goodnessb{property \textbf{(!')}}
\newcommand\goodnessbshort{\textbf{(!')}}
\newcommand\isgoodb{has property \textbf{(!')}}
\newcommand\aregoodb{have property \textbf{(!')}}
\newcommand\goodbX[1]{#1 with property \textbf{(!')}}

\newcommand\dualize{\mathbb D}

@@

\begin{document}

\maketitle

[macros]

\begin{abstract}
    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
\end{abstract}

@@

Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).

@@

This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.

@@

In this paper we investigate how to quantify the cone of the morphism
\begin{equation}\label{eq:intro:central_cone}
    p_{1,!}p₂^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\end{equation}
and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:main}
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

Since, to the author's knowledge, there is currently no comprehensive account of the theory of D-modules on stacks available in the literature, we review the basic formalism in Section~\ref{sec:d-mods}.
In essence, most of the familiar six functor formalism of holonomic D-modules works in a general context.
It is convenient to rephrase Theorem~\ref{thm:main} as an equivalence of monads.
Thus in Section~\ref{sec:monads} we review some constructions of monads in our setting.
In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.

In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.

The present paper represents only the first step in the study of Hochschild cohomology and associated support theories for D-modules.
In future work we intend to expand upon the foundations laid out in this paper.
Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
Following the constructions laid out in Section~\ref{sec:base-change:compactification}, for the former we need a good $G×G$-equivariant compactification of $G$.
Thus groups with a wonderful compactification are of particular interest for study with our methods.
For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.% \cite{Gaitsgory:preprint:StrangeFunctionalEquationForEisensteinSeries}

\subsection*{Acknowledgments}
I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.

\section{D-modules on stacks}
\label{sec:d-mods}

@@

In order to correctly define categories of D-modules on stacks it is necessary to work with dg-categories.
We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction.% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}. %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.

The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.

For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
If $p\colon \stack X → \pt$ is the structure map, we set
\[
    \GammadR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
\]
The functor $\GammadR$ is representable by a D-module $k_{\stack X}$, i.e.
\[
    \GammadR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
\]
As $\GammadR(\stack X,\, {-})$ is usually not continuous and the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.

@@

\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
    \label{prop:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
\end{Prop}

@@

It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.
For quotient stacks we give the resulting subcategory a special name.

\begin{Def}
    \label{def:pre:monodromic}%
    Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
    The \emph{monodromic} subcategory $\catDModMon{X}{G} ⊆ \catDMod{X}$ is the full subcategory generated by the essential image of $p^!\colon \catDMod{X/G} → \catDMod{X}$ (or equivalently by the essential image of $p^*$).
\end{Def}

In Section~\ref{sec:torus} we will be concerned with $\Gm^n$-monodromic D-modules.
For the case of $n = 1$ one has the following powerful theorem, known as the \emph{contraction principle}.
It will be a crucial ingredient for our proof of Theorem~\ref{thm:main}.

\begin{Thm}[{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is a canonical isomorphism of functors
    \[
        π_* \cong i^* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}
    \]
    given by adjunction
    \[
        π_* → π_* i_* i^* = (π ∘ i)_* i^* = i^*.
    \]
\end{Thm}

\section{Monads}
\label{sec:monads}

@@

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the dg vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.

The most common source of monads is from a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
\[
    \id[\cat C] → G ∘ F = T
    \qquad\text{and}\qquad
    T² = G ∘ (F ∘ G) ∘ F → G ∘ F = T.
\]
We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2014-draft:HigherAlgebra}.
For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
\[
    \Hom_{\cat C}(X, (GF)(X)) \cong
    \Hom_{\cat D}(FX, FX).
\]

@@

The Beck--Chevalley condition us formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
\[
    \stack G_i = \underbrace{\stack G₁ ×_{\stack G₀} \dotsb ×_{\stack G₀} \stack G₁}_{\text{$i$ factors}}.
\]
We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.

@@

\section{Torus quotients}
\label{sec:torus}

>>>>

\title{Hochschild cohomology of torus equivariant D-modules}
\author{Clemens Koppensteiner}

%\usepackage{math-ag}

@@

% overrides
\let\shortbar\bar
\let\bar\overline

% spaces
\newcommand\as[2][]{\mathbb A^{#2}_{#1}}    % affine space
\newcommand\ps[2][]{\mathbb P^{#2}_{#1}}    % projective space
\newcommand\pt{\mathrm{pt}}                 % a point
\newcommand\Ga{\mathbb{G}_{\mathrm{a}}}     % G_a
\newcommand\Gm{\mathbb{G}_{\mathrm{m}}}     % G_m
\DeclareMathOperator\Spec{Spec}

% stacks
\let\stack\mathbf                           % basic formatting for stacks
\newcommand\cs{\stack{B}}                   % classifying stack
\newcommand\LocSys{\operatorname{LocSys}}   % local systems
\newcommand\Bun{\operatorname{Bun}}         % bundles

% category theory and homological algebra
\newcommand\cat{\mathbf}                    % formatting for categories
\newcommand\catCoSimplicial{\Delta^{\mathrm{op}}}
\DeclareMathOperator\Hom{Hom}
\newcommand\id[1][]{{\mathrm{Id}_{#1}}}     % identity map
\newcommand\catVect[1][]{\cat{Vect}_{#1}}   % vector spaces
\newcommand\catModules[1]{\cat{Mod}(#1)}    % modules over a ring, etc.
\newcommand\cx\bullet                       % dot for complexes
\newcommand\dual{∨}
\newcommand\cocolon{%                       % mirrored \colon (for an adjunction)
    \nobreak \mskip 6muplus1mu \mathpunct {}\nonscript \mkern -\thinmuskip{:}\mskip 2mu\relax%
}
\newcommand\rquot[2]{%                      % quotient on the right
    \mathchoice%
        {\left.#1\kern-0.2ex\middle/\kern-0.3ex\lower0.7ex\hbox{$\displaystyle #2$}\right.}%
        {\left.#1\middle/#2\right.}%
        {\left.#1\middle/#2\right.}%
        {\left.#1\middle/#2\right.}%
}
\newcommand\isoto\similarrightarrow         % isomorphisms
\newcommand\proj[1]{\operatorname{pr}_{#1}} % projection on a factor
\newcommand{\HCoh}{\operatorname{HH}^\cx}   % Hochschild cohomology

% Sheaves and D-modules
\newcommand\sheaf\mathscr
\DeclareMathOperator\supp{supp}     % support
\newcommand\catDMod[2][]{\cat{DMod}_{#1}(#2)}   % category of D-modules
\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}   % holonomic D-modules
\newcommand\dR{\mathrm{dR}}
\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
\newcommand{\renstar}{\blacktriangle}
\newcommand\dualize{\mathbb D}
\newcommand\catIndCoh[2][]{\cat{IndCoh}_{#1}(#2)} % category of ind-coherent sheaves

\newcommand\opalg[1]{#1^{\mathrm{op}}}
\newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
\newcommand\barGammasub[1]{\bar{\Gamma}_{\mkern-3mu#1}}

\newcommand\XXtimes{%
    \mathchoice%
        {\mathop{×}\limits_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
    }

\newcommand\bc{\textbf{($\mathbf{*}$)}}
\newcommand\hbc{\textbf{($\mathbf{**}$)}}

\newcommand\catK[2][]{\cat{K}_{#1}(#2)}
\newcommand\catKHol[1]{\catK[\mathrm{hol}]{#1}}

\newcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}

@@

\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}

@@

\begin{document}
\maketitle

\begin{abstract}
  We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic stack.
  In particular we describe the Hochschild cohomology of the category of torus-equivariant D-modules as the cohomology of a D-module on the loop space of the quotient stack.
  Finally, we give an approach for understanding the Hochschild cohomology of D-modules on general stacks via a relative compactification of the diagonal.
  This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
\end{abstract}

@@

Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
For co-complete compactly generated triangulated categories one answer is provided by Benson, Iyengar and Krause \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
To each map from a graded-commutative ring $R$ to the center of $\cat C$ one associates the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves mentioned above).

@@

This construction, applied to the category of (ind-)coherent sheaves on a (quasi-smooth, dg-) scheme, yields the singular support of coherent sheaves introduced by Arinkin and Gaitsgory \cite{ArinkinGaitsgory:2015:SingularSupport}.
The authors use this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
Thanks to the theory of integral kernels, this question can be approached geometrically.
Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.

@@

In this paper we investigate the morphism
\begin{equation}\label{eq:intro:central_cone}
    p_{1,!}p₂^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\end{equation}
and thus when the naive isomorphism \eqref{eq:intro:naive} holds.
As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:main}
    Let $G \cong \Gm^n$ be a torus acting on a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

\subsection*{Contents}

Since, to the author's knowledge, there is currently no comprehensive account of the theory of D-modules on stacks available in the literature, we review the basic formalism in Section~\ref{sec:d-mods}.
In essence, most of the familiar six functor formalism of holonomic D-modules works in a general context.
It is convenient to rephrase Theorem~\ref{thm:main} as an equivalence of monads.
Thus in Section~\ref{sec:monads} we review some constructions of monads in our setting.
In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
As a simple application of this formalism, we also show that $\HCoh{\catDMod{\stack X}}$ always has a subalgebra isomorphic to $\opalg{\GammadR(\stack X,\ k_{\stack X})}$.

In Section~\ref{sec:base-change} we give a criterion for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite[Section~5.1]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} to understand the case of so-called contractive stacks.
Using the theory developed in Section~\ref{sec:base-change}, the proof of Theorem~\ref{thm:main} is given in Section~\ref{sec:torus}.

Finally, in Section~\ref{sec:compactification} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.

\subsection*{Future directions}

The present paper represents only the first step in the study of Hochschild cohomology and associated support theories for D-modules.
In future work we intend to expand upon the foundations laid out in this paper.
Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
Following the constructions laid out in Section~\ref{sec:compactification:quotient}, for the former we need a good $G×G$-equivariant compactification of $G$.
Thus groups with a wonderful compactification are of particular interest for study with our methods.
For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.% \cite{Gaitsgory:preprint:StrangeFunctionalEquationForEisensteinSeries}

\subsection*{Acknowledgments}
I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.
I would also like to thank David Ben-Zvi, Dennis Gaitsgory and Nathan Ilten for discussions concerning this project.
This work has been partially supported by the National Science Foundation under Grant No.~1638352, as well as the Giorgio and Elena Petronio Fellowship Fund.

\section{D-modules on stacks}\label{sec:d-mods}

@@

In order to correctly define categories of D-modules on stacks it is necessary to work with dg-categories.
We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2017-draft:HigherAlgebra}, which can be done via the nerve construction. % \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}. %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2017-draft:HigherAlgebra} to dg categories.
Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.

The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
It is explained in detail in the book \cite{GaitsgoryRozenblyum:2017:StudyInDAG:2} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.

For any morphism $f\colon \stack X → \stack Y$ we have a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
If $p\colon \stack X → \pt$ is the structure map, we set
\[
    \GammadR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
\]
The functor $\GammadR$ is representable by a D-module $k_{\stack X}$, i.e.
\[
    \GammadR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
\]
As $\GammadR(\stack X,\, {-})$ is usually not continuous the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.

@@

\begin{Prop}[{\cite[Section~4.2.1.3]{GaitsgoryRozenblyum:2017:StudyInDAG:2}}]
    \label{prop:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence also schematic $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
    Similarly, if $f$ is an open immersion, then the base change isomorphism coincides with the natural transformation resulting from the adjunctions $(f^!,f_*)$ and $(p^!, p_*)$.
\end{Prop}

@@

\section{Monads}\label{sec:monads}

@@

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2017-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the dg vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\eqref{eq:pre:monad-identities} ensure that the algebra is associative and unital.

The most common source of monads is a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
\[
    \id[\cat C] → G ∘ F = T
    \qquad\text{and}\qquad
    T² = G ∘ (F ∘ G) ∘ F → G ∘ F = T.
\]
We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2017-draft:HigherAlgebra}.
For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
\[
    \Hom_{\cat C}(X, (GF)(X)) \cong
    \Hom_{\cat D}(FX, FX).
\]

@@

The Beck--Chevalley condition is formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
\[
    \stack G_i = \underbrace{\stack G₁ ×_{\stack G₀} \dotsb ×_{\stack G₀} \stack G₁}_{\text{$i$ factors}}.
\]
We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
The following lemma is now an immediate corollary of \cite[Lemma~4.7.1.4]{GaitsgoryRozenblyum:2017:StudyInDAG:2} or \cite[Theorem~4.7.5.2]{Lurie:2017-draft:HigherAlgebra}.

@@
